---
title: "HBR_watershed_4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Step 1: Load packages
```{r}

library(metajam)  
library(udunits2)
# For wrangling the data
library(readr)
library(tidyr)
library(dplyr)
library(purrr)
library(stringr)
library(metajam)
library(tidyverse) # for convenience
library(here) # for file path management
library(stringdist) # for first pass of naming-matching
library(vctrs) # for joining tables
library(readxl) # for reading the template excel sheet



```

####Step 2: Find the link to the dataset
Go to the web address for the dataset and find the download button for the data. 

In our case the link is: https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-hbr.6.15&entityid=693eaf5a834ae7fecc5111a5ce0a420b

#### Step 3: Choose where you want the files to be saved
In our case, we'll just put it into the metajam_example folder.
```{r}

#eg desired_path_to_data <- "~/Desktop"
desired_path_to_data <- "~/SI_river_data"

# create the folder if it does not exist yet
dir.create(desired_path_to_data, showWarnings = FALSE)

```

#### Step 4: Download the data by pasting the link you just copied

```{r}

my_data_url <- "https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-hbr.6.15&entityid=693eaf5a834ae7fecc5111a5ce0a420b"

# this will download the data into a folder and save the path to that folder
downloaded_data <- download_d1_data(data_url = my_data_url, path = desired_path_to_data)

```

#### Step 5: Now read in the data (with all the metadata)

```{r}

my_data <- read_d1_files(downloaded_data, na = c("-888.88", "-888.888", "-888"))

HBR_watershed_4_data <- my_data$data


```

###Step 6: data cleanup

```{r}

#There are 652 rows in this df
#Adding a column to identify the LTER site - Hubbar Brook HBR

# the tidy way
HBR_watershed_4_data <- HBR_watershed_4_data %>% 
  add_column(LTER = 'HBR', .before = "Year")

#There is no site name in the csv file so I pulled this site identifier from the data portal

HBR_watershed_4_data <- HBR_watershed_4_data %>% 
  add_column('Site/Stream Name' = 'knb-lter-hbr.6.15', .before = "Year")

# I can see that the column Year_Month includes the info from the column in the template 'Sampling Date' so I want to rename that column 

HBR_watershed_4_data <- HBR_watershed_4_data %>% 
  rename('Sampling Date' = 'Year_Month')

```

```{r}

#Removing the volwt_ preface from many of the column names. That preface was preventing me from identifying which columns were a match to the template 

names(HBR_watershed_4_data)[7:31] <- substring(names(HBR_watershed_4_data)[7:31],7,15)

#SpecCond is a match for the template column 'Spec Cond' i just need to make them match exactly
HBR_watershed_4_data <- HBR_watershed_4_data %>% 
  rename('Spec Cond' = 'SpecCond')

HBR_watershed_4_data <- HBR_watershed_4_data %>% 
  rename('DSi' = 'SiO2')

```

Read in template
```{r}


template <- read_excel(here("metajam_example", "Raw stream data template.xlsx"), 
                               col_types = "text"
                               ) %>%
  mutate(`Sampling Date` = as.Date(`Sampling Date`))

```

Fuzzy match

```{r}

# Start by matching by closest name as a first pass. 
  # Note that we match the lower case names
  # Note that the weight i= 0.1 says that we will be more likely to match if watershed 1 = template + extra
(fuzzy_match <- tibble(template = names(template)) %>%
   mutate(watershed4 = names(HBR_watershed_4_data)[amatch(tolower(template), tolower(names(HBR_watershed_4_data)), maxDist = 1, weight = c(d=1,i=0.1,s=1,t=1))])
)


(lookup_table <- fuzzy_match %>%
  mutate(watershed4 = case_when(
    template %in% c("DIN", "TN", "NOx",  "TOC") ~ NA_character_,
    TRUE ~ watershed4)))

correct_colnames <- lookup_table$template



```

```{r}


lookup_table <- lookup_table %>%
  filter(!is.na(watershed4))

correct_colnames <- lookup_table$template

new_datatable4 <- HBR_watershed_4_data %>% 
        select(one_of(c(correct_colnames)))



```


Loading the solute units template

```{r}


solute_units_Template <- read_excel(here("metajam_example", "Stream_Data_Template.xlsx"), sheet = "Solute Units" )

solute_units_Template <- solute_units_Template  %>%
  select(Measurement, Unit)


```

Making a dataframe from the attribute metadata that only inlcudes the columns I need to match the template (aatributeName and units)
```{r}

attributes <- data.frame(my_data$attribute_metadata)

attributes <- attributes  %>%
  select(attributeName, unit)

#Removing the "volwt_" preface from the attribute names so that I can match them
attributes$attributeName <- gsub("volwt_", "", attributes$attributeName)

attributes$attributeName <- gsub("SpecCond", "Specific Conductance", attributes$attributeName)

```



Fuzzy matching template solute units table to attribute table
```{r}

(fuzzy_match <- tibble(solute_units_Template$Measurement) %>%
   mutate(watershed_units_4 = attributes$attributeName[amatch(tolower(solute_units_Template$Measurement), tolower(attributes$attributeName), maxDist = 1, weight = c(d=1,i=0.1,s=1,t=1))])
)

fuzzy_match$watershed_units_4 <- gsub("SiO2", "Si", fuzzy_match$watershed_units_4)

```


```{r}


# Fill in the columns that didn't match, and correct the wrongly corrected matches
# continue in the same way until you've filled out everything you could.
  # Note: NA_character_ is just NA but of the character type.
(lookup_table_units <- fuzzy_match %>%
  mutate(watershed_units_4 = case_when(
    solute_units_Template$Measurement %in% c("DO","Q", "DO%","TOC", "TDP","PON", "PP", "TKN","DOP","TN", "TP") ~ NA_character_,
    TRUE ~ watershed_units_4)))

#Make a string of the correct names
correct_names <- lookup_table_units$'solute_units_Template$Measurement'


```

```{r}

#Make a table that matches the template
solute_units_table_new <- attributes %>% 
        filter(attributeName %in% c(correct_names))

solute_units_table_new  %>% 
  rename(Measurement = attributeName, Unit = unit)
```

Export an excel workbook with two sheets

```{r}


## setup a workbook with 2 worksheets
wb <- createWorkbook()
addWorksheet(wb = wb, sheetName = "Raw Data (Sheet 1)", gridLines = FALSE)

writeDataTable(wb = wb, sheet = 1, x = new_datatable4)

addWorksheet(wb = wb, sheetName = "Solute Units (Sheet 2)", gridLines = FALSE)

writeData(wb = wb, sheet = 2, x = solute_units_table_new)

saveWorkbook(wb, "HBR_4_watershed.xlsx", overwrite = TRUE)

```

What proportion of cells in the new data table are NA?

```{r}

sum(is.na(new_datatable4))/prod(dim(new_datatable4))

#for columns
colMeans(is.na(new_datatable4))

```


