---
title: "HBR_watershed_10"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


###Step 1: Load packages
```{r}

library(metajam)  
library(udunits2)
# For wrangling the data
library(readr)
library(tidyr)
library(dplyr)
library(purrr)
library(stringr)
library(metajam)
library(tidyverse) # for convenience
library(here) # for file path management
library(stringdist) # for first pass of naming-matching
library(vctrs) # for joining tables
library(readxl) # for reading the template excel sheet
library(naniar)
library(openxlsx)

```


####Step 2: Find the link to the dataset
Go to the web address for the dataset and find the download button for the data. 

In our case the link is: https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-nwt.103.12&entityid=413c3eb5a1a52e3ce2f9e52b3565aadd

#### Step 3: Choose where you want the files to be saved
In our case, we'll just put it into the metajam_example folder.

```{r}

albisolu_NWT_data <- data_from_EDI(my_data_url = "https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-nwt.103.12&entityid=413c3eb5a1a52e3ce2f9e52b3565aadd", desired_path_to_data = "~/SI_river_data")


```


###Step 6: data cleanup

```{r}

albisolu_NWT_data <- EDI_river_data_cleanup(my_dataframe = albisolu_NWT_data)

```



Read in template
```{r}

template <- import_river_data_template()

```

Fuzzy match
```{r}

# Start by matching by closest name as a first pass. 
  # Note that we match the lower case names
  # Note that the weight i= 0.1 says that we will be more likely to match if watershed 1 = template + extra

fuzzymatch_river_data(river_template_name = template, data_name = albisolu_NWT_data)

```

```{r}


# Fill in the columns that didn't match, and correct the wrongly corrected matches
# continue in the same way until you've filled out everything you could.
  # Note: NA_character_ is just NA but of the character type.
(lookup_table <- fuzzy_match %>%
  mutate(watershed10 = case_when(
    template %in% c("DIN", "NOx", "DIC") ~ NA_character_,
    TRUE ~ watershed10)))

lookup_table <- lookup_table %>%
  filter(!is.na(watershed10))

correct_colnames <- lookup_table$template

correct_colnames <- as.character(correct_colnames)


```
Once the lookup table is as filled out as possible, we can remove all rows that still had no match.

```{r}


new_datatable_NWT_1 <- albisolu_NWT_data %>% 
        select(all_of(c(correct_colnames)))


```

```{r}




#Changing missing value codes for columns for which NP is the missing value code

#new_datatable_NWT_1 <- new_datatable_NWT_1 %>% 
 #mutate(NH4 = ifelse(NH4 < 0.1428, NA, NH4))

#new_datatable_NWT_1 <- new_datatable_NWT_1 %>% 
#mutate(PO4 = ifelse(PO4 < 0.0387, NA, PO4))

#new_datatable_NWT_1 <- new_datatable_NWT_1 %>% 
#mutate(TDP = ifelse(TDP < 0.0258, NA, TDP))

#new_datatable_NWT_1 <- new_datatable_NWT_1 %>% 
# mutate(Cl = ifelse(Cl < 0.28, NA, Cl))


```


Loading the solute units template

```{r}

solute_units_Template  <- import_solute_units_template()

```

Making a dataframe from the attribute metadata that only inlcudes the columns I need to match the template (attributeName and units)
```{r}

attributes <- data.frame(my_data$attribute_metadata)

attributes <- attributes  %>%
  select(attributeName, unit)

#Changing some attribute names so that they are easier to match

attributes$attributeName <- gsub("cond", "Conductivity", attributes$attributeName)

attributes$attributeName <- gsub("alkal", "Alkalinity", attributes$attributeName)

#Remove ionic notations
attributes$attributeName <- gsub("[^0-9A-Za-z///' ]"," ", attributes$attributeName)

```



Fuzzy matching template solute units table to attribute table
```{r}

(fuzzy_match <- tibble(solute_units_Template$Measurement) %>%
   mutate(watershed_units_10 = attributes$attributeName[amatch(tolower(solute_units_Template$Measurement), tolower(attributes$attributeName), maxDist = 1, weight = c(d=1,i=0.1,s=1,t=1))])
)


```


```{r}


# Fill in the columns that didn't match, and correct the wrongly corrected matches
# continue in the same way until you've filled out everything you could.
  # Note: NA_character_ is just NA but of the character type.
(lookup_table_units <- fuzzy_match %>%
  mutate(watershed_units_10 = case_when(
    solute_units_Template$Measurement %in% c("DIC","DO", "DO%", "TKN", "PON") ~ NA_character_,
    TRUE ~ watershed_units_10)))

#Make a string of the correct names
correct_names <- lookup_table_units$'solute_units_Template$Measurement'


```

```{r}

#Make a table that matches the template
solute_units_table_new <- attributes %>% 
        filter(attributeName %in% c(correct_names))

solute_units_table_new  %>% 
  rename(Measurement = attributeName, Unit = unit)

```

Export an excel workbook with two sheets

```{r}


## setup a workbook with 2 worksheets
wb <- createWorkbook()
addWorksheet(wb = wb, sheetName = "Raw Data (Sheet 1)", gridLines = FALSE)

writeDataTable(wb = wb, sheet = 1, x = new_datatable_NWT_1)

addWorksheet(wb = wb, sheetName = "Solute Units (Sheet 2)", gridLines = FALSE)

writeData(wb = wb, sheet = 2, x = solute_units_table_new)

saveWorkbook(wb, "NWT_albisolu_watershed.xlsx", overwrite = TRUE)

```

What proportion of cells in the new data table are NA?

```{r}

sum(is.na(new_datatable_NWT_1))/prod(dim(new_datatable_NWT_1))

#for columns
colMeans(is.na(new_datatable_NWT_1))

```
