---
title: "ADC_Toolik_duplicates"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Step 1: Load packages

```{r}

library(metajam)  
library(udunits2)
# For wrangling the data
library(readr)
library(tidyr)
library(dplyr)
library(purrr)
library(stringr)
library(metajam)
library(tidyverse) # for convenience
library(here) # for file path management
library(stringdist) # for first pass of naming-matching
library(vctrs) # for joining tables
library(readxl) # for reading the template excel sheet
library(openxlsx) #for writing the excel file
library(expss)

```

####Step 2: Find the link to the dataset
Go to the web address for the dataset and find the download button for the data. 

In our case the link is: https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-arc.10303.6&entityid=bbc1cb59633df57380d997726916180a

#### Step 3: Choose where you want the files to be saved
In our case, we'll just put it into the metajam_example folder.

```{r}

#eg desired_path_to_data <- "~/Desktop"
desired_path_to_data <- "~/SI_river_data"

# create the folder if it does not exist yet
dir.create(desired_path_to_data, showWarnings = FALSE)

```

#### Step 4: Download the data by pasting the link you just copied
```{r}

my_data_url <- "https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-arc.10303.6&entityid=bbc1cb59633df57380d997726916180a"

# this will download the data into a folder and save the path to that folder
downloaded_data <- download_d1_data(data_url = my_data_url, path = desired_path_to_data)


```

#### Step 5: Now read in the data (with all the metadata)

```{r}


my_data <- read_d1_files(downloaded_data, na = c("-888.88", "-888.888", "-888", "-999", "-9999", "u", "NP"))

Toolik_watershed_data <- my_data$data

#remove 2nd and 3rd rows which were empty
Toolik_watershed_data <-  Toolik_watershed_data[-c(1, 2, 3),]

my_data$attribute_metadata

```

#Data Cleanup


```{r}

#removing colons and dashes from attribute column names
Toolik_watershed_data$Type <- gsub("[^0-9A-Za-z///' ]","", Toolik_watershed_data$Type)

#removing cation preface
Toolik_watershed_data$Type <- gsub("Cations", "", Toolik_watershed_data$Type)

#strip white space
Toolik_watershed_data$Type  <- trimws(Toolik_watershed_data$Type, which = c("left"))


#Adding a column to identify the LTER site - ARC
Toolik_watershed_data <- Toolik_watershed_data %>% 
  add_column(LTER = 'ARC', .before = "River")

#all watershed except the fog lake series
Toolik_rivers_watershed <- Toolik_watershed_data %>% 
 filter(River %in% c("Birthday Creek", "Burn Reference Streams", "Caterpillar Creek", "Caterpillar Creek TK", "Dimple Inlet", "Dimple Outlet", "I-Minus 2", "I-Minus 2 TK", "Imnavait Creek", "Itkillik Tributary", "Kuparuk River", "North River", "Oksrukuyik Creek", "Roche Moutonnee Creek", "Shrew River", "South River", "South River Trib", "Toolik Inlet","Toolik River", "Toolik River TK", "Toolik River TK-4", "Trevor Creek", "Upper Kuparuk", "VTK IMP", "VTK REF"))

#Unsure what the 'Site/Stream Name' should be so combining river name and station
Toolik_rivers_watershed  <- Toolik_rivers_watershed  %>% 
add_column('Site/Stream Name' = paste(Toolik_rivers_watershed$River, Toolik_rivers_watershed$Station), .before = 'River')


```

Making a table with comments column so I can add it back later. If I keep the comments column in the datetable R fails to detect duplicate values (because the duplicate has 'ISCO' in the comments field)

```{r}

#cleaning up duplicates file to share
Toolik_rivers_watershed_COMMENTS   <- Toolik_rivers_watershed  %>% 
  select(-'Site Code', -'Station', -'Reach', -'Method / Instrument', -'Units', -'River')  %>% 
  rename('Sampling Date' = 'Date') 

Toolik_rivers_watershed_COMMENTS  <-  add_column(.data = Toolik_rivers_watershed_COMMENTS, 'Time' = substr(Toolik_rivers_watershed_COMMENTS$`Sampling Date`, 11, 16), .after = 'Sampling Date')

#removing time from sampling date column
Toolik_rivers_watershed_COMMENTS   <- Toolik_rivers_watershed_COMMENTS  %>% 
  mutate('Sampling Date' = substr(Toolik_rivers_watershed_COMMENTS$`Sampling Date`, 1, 10))

#distinct df that highlights the duplicates
Toolik_watershed_with_COMMENTS<- pivot_wider(Toolik_rivers_watershed_COMMENTS, names_from = 'Type', values_from = 'Value')



```



```{r}


#cleaning up duplicates file to share
Toolik_watershed_with_duplicates   <- Toolik_rivers_watershed %>% 
  select(-'Site Code', -'Station', -'Reach', -'Method / Instrument', -'Units', -'River', -'Comments')  %>% 
  rename('Sampling Date' = 'Date')

#distinct df that highlights the duplicates
Toolik_watershed_with_duplicates <- pivot_wider(Toolik_watershed_with_duplicates, names_from = 'Type', values_from = 'Value')

#extracting 'time' from sampling date column and making it it's own column
Toolik_watershed_with_duplicates   <- add_column(.data = Toolik_watershed_with_duplicates, 'Time' = substr(Toolik_watershed_with_duplicates$`Sampling Date`, 11, 16), .after = 'Sampling Date')

#removing time from sampling date column
Toolik_watershed_with_duplicates  <- Toolik_watershed_with_duplicates %>% 
  mutate('Sampling Date' = substr(Toolik_watershed_with_duplicates$`Sampling Date`, 1, 10))

#Renaming columns to match template abbreviations
Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates  %>% 
  rename('Ca' = 'Calcium', 'Spec Cond' = 'Specific Conductivity', 'Na' = 'Sodium', 'K' = 'Potassium', 'Mg' = 'Magnesium', 'TDP' = 'Total Dissolved Phosphorus', 'DOC' = 'Dissolved Organic Carbon', 'NH4' = 'Ammonium', 'TDN' = 'Total Dissolved Nitrogen', 'Suspended Chl' = 'Sestonic Chlorophyll a', 'Temp C' = 'Temp when sample collected', 'SRP' = 'Soluble Reactive Phosphorus', 'Cl' = 'Chloride', 'alkalinity' = 'Alkalinity', 'Pb' = 'Lead', 'Fe' = 'Iron', 'SO4' = 'Sulfate', 'Cu' = 'Copper', 'TSS' = 'Total Suspended Sediment', 'CO2' = 'Carbon Dioxide', 'DIC' = 'Dissolved Inorganic Carbon', 'CH4' = 'Methane', 'NOx' = 'NitrateNitrite')


Toolik_watershed_with_duplicates2 = sapply(Toolik_watershed_with_duplicates[6:20],
              function(x) grep(",", x, value = TRUE))


attributes_with_duplicates <- names(Toolik_watershed_with_duplicates2)


```
Cleaning up columns

```{r}


Toolik_watershed_with_duplicates$alkalinity <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$alkalinity)

Toolik_watershed_with_duplicates$alkalinity <- gsub("c","", Toolik_watershed_with_duplicates$alkalinity)


```


```{r}


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate(alkalinity, c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'alkalinity' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$alkalinity <- na_if(Toolik_watershed_with_duplicates$alkalinity, 'NaN')



```
Ran this multiple times, for each of the attributes listed in "attributes_with_duplicates" vector

NH4

```{r}


Toolik_watershed_with_duplicates$'NH4' <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$'NH4')

Toolik_watershed_with_duplicates$'NH4' <- gsub("c","", Toolik_watershed_with_duplicates$'NH4')


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate('NH4', c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'NH4' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$'NH4' <- na_if(Toolik_watershed_with_duplicates$'NH4', 'NaN')


```

```{r}



Toolik_watershed_with_duplicates$'CO2' <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$'CO2')

Toolik_watershed_with_duplicates$'CO2' <- gsub("c","", Toolik_watershed_with_duplicates$'CO2')


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate('CO2', c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'CO2' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$'CO2' <- na_if(Toolik_watershed_with_duplicates$'CO2', 'NaN')


```
```{r}

Toolik_watershed_with_duplicates$'Ca' <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$'Ca')

Toolik_watershed_with_duplicates$'Ca' <- gsub("c","", Toolik_watershed_with_duplicates$'Ca')


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate('Ca', c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'Ca' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$'Ca' <- na_if(Toolik_watershed_with_duplicates$'Ca', 'NaN')


```

```{r}

Toolik_watershed_with_duplicates$'Mg' <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$'Mg')

Toolik_watershed_with_duplicates$'Mg' <- gsub("c","", Toolik_watershed_with_duplicates$'Mg')


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate('Mg', c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'Mg' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$'Mg' <- na_if(Toolik_watershed_with_duplicates$'Mg', 'NaN')


```
```{r}

Toolik_watershed_with_duplicates$'K' <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$'K')

Toolik_watershed_with_duplicates$'K' <- gsub("c","", Toolik_watershed_with_duplicates$'K')


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate('K', c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'K' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$'K' <- na_if(Toolik_watershed_with_duplicates$'K', 'NaN')

```

```{r}

View(attributes_with_duplicates)

```


```{r}

Toolik_watershed_with_duplicates$'Na' <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$'Na')

Toolik_watershed_with_duplicates$'Na' <- gsub("c","", Toolik_watershed_with_duplicates$'Na')


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate('Na', c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'Na' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$'Na' <- na_if(Toolik_watershed_with_duplicates$'Na', 'NaN')

```

```{r}

Toolik_watershed_with_duplicates$'DOC' <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$'DOC')

Toolik_watershed_with_duplicates$'DOC' <- gsub("c","", Toolik_watershed_with_duplicates$'DOC')


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate('DOC', c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'DOC' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$'DOC' <- na_if(Toolik_watershed_with_duplicates$'DOC', 'NaN')



```

```{r}

Toolik_watershed_with_duplicates$'CH4' <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$'CH4')

Toolik_watershed_with_duplicates$'CH4' <- gsub("c","", Toolik_watershed_with_duplicates$'CH4')


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate('CH4', c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'CH4' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$'CH4' <- na_if(Toolik_watershed_with_duplicates$'CH4', 'NaN')


```
```{r}

Toolik_watershed_with_duplicates$'NOx' <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$'NOx')

Toolik_watershed_with_duplicates$'NOx' <- gsub("c","", Toolik_watershed_with_duplicates$'NOx')


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate('NOx', c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'NOx' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$'NOx' <- na_if(Toolik_watershed_with_duplicates$'NOx', 'NaN')


```

```{r}


Toolik_watershed_with_duplicates$'Suspended Chl' <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$'Suspended Chl')

Toolik_watershed_with_duplicates$'Suspended Chl' <- gsub("c","", Toolik_watershed_with_duplicates$'Suspended Chl')


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate('Suspended Chl', c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'Suspended Chl' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$'Suspended Chl' <- na_if(Toolik_watershed_with_duplicates$'Suspended Chl', 'NaN')


```

```{r}


Toolik_watershed_with_duplicates$'Sestonic Particulate Carbon' <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$'Sestonic Particulate Carbon')

Toolik_watershed_with_duplicates$'Sestonic Particulate Carbon' <- gsub("c","", Toolik_watershed_with_duplicates$'Sestonic Particulate Carbon')


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate('Sestonic Particulate Carbon', c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'Sestonic Particulate Carbon' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$'Sestonic Particulate Carbon' <- na_if(Toolik_watershed_with_duplicates$'Sestonic Particulate Carbon', 'NaN')


```
```{r}

Toolik_watershed_with_duplicates$'Sestonic Particulate Nitrogen' <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$'Sestonic Particulate Nitrogen')

Toolik_watershed_with_duplicates$'Sestonic Particulate Nitrogen' <- gsub("c","", Toolik_watershed_with_duplicates$'Sestonic Particulate Nitrogen')


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate('Sestonic Particulate Nitrogen', c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'Sestonic Particulate Nitrogen' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$'Sestonic Particulate Nitrogen' <- na_if(Toolik_watershed_with_duplicates$'Sestonic Particulate Nitrogen', 'NaN')


```

```{r}

Toolik_watershed_with_duplicates$'Sestonic Particulate Phosphorus' <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$'Sestonic Particulate Phosphorus')

Toolik_watershed_with_duplicates$'Sestonic Particulate Phosphorus' <- gsub("c","", Toolik_watershed_with_duplicates$'Sestonic Particulate Phosphorus')


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate('Sestonic Particulate Phosphorus', c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'Sestonic Particulate Phosphorus' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$'Sestonic Particulate Phosphorus' <- na_if(Toolik_watershed_with_duplicates$'Sestonic Particulate Phosphorus', 'NaN')


```


```{r}


	

Toolik_watershed_with_duplicates$'Sestonic Phaeopigment' <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$'Sestonic Phaeopigment')

Toolik_watershed_with_duplicates$'Sestonic Phaeopigment' <- gsub("c","", Toolik_watershed_with_duplicates$'Sestonic Phaeopigment')


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate('Sestonic Phaeopigment', c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'Sestonic Phaeopigment' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$'Sestonic Phaeopigment' <- na_if(Toolik_watershed_with_duplicates$'Sestonic Phaeopigment', 'NaN')


```




```{r}

Toolik_watershed_with_duplicates$'Silica' <- gsub("[[:punct:]]","", Toolik_watershed_with_duplicates$'Silica')

Toolik_watershed_with_duplicates$'Silica' <- gsub("c","", Toolik_watershed_with_duplicates$'Silica')


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  separate('Silica', c("A", "B", "C"),sep=" ") 

Toolik_watershed_with_duplicates$A <- as.numeric(Toolik_watershed_with_duplicates$A)
Toolik_watershed_with_duplicates$B <- as.numeric(Toolik_watershed_with_duplicates$B)
Toolik_watershed_with_duplicates$C <- as.numeric(Toolik_watershed_with_duplicates$C)


Toolik_watershed_with_duplicates  <- cbind(Toolik_watershed_with_duplicates ,'Silica' =rowMeans(Toolik_watershed_with_duplicates[5:7], na.rm=TRUE))


Toolik_watershed_with_duplicates <- Toolik_watershed_with_duplicates %>% 
  select(-'A', -'B', -'C')

Toolik_watershed_with_duplicates$'Silica' <- na_if(Toolik_watershed_with_duplicates$'Silica', 'NaN')


```


Read in template. Doulbe check the template is correct!
```{r}

template <- read_excel(here("metajam_example", "Raw stream data template.xlsx"), 
                               col_types = "text"
                               ) %>%
  mutate(`Sampling Date` = as.Date(`Sampling Date`))  %>% 
  add_column('Comments' = ' ')

#names(template)

```

Fuzzy Match
```{r}


# Start by matching by closest name as a first pass. 
  # Note that we match the lower case names
  # Note that the weight i= 0.1 says that we will be more likely to match if watershed 1 = template + extra
(fuzzy_match <- tibble(template = names(template)) %>%
   mutate(watershed_toolik_all = names(Toolik_watershed_with_duplicates)[amatch(tolower(template), tolower(names(Toolik_watershed_with_duplicates)), maxDist = 1, weight = c(d=1,i=0.1,s=1,t=1))])
)

```

```{r}


# Fill in the columns that didn't match, and correct the wrongly corrected matches
# continue in the same way until you've filled out everything you could.
  # Note: NA_character_ is just NA but of the character type.
(lookup_table <- fuzzy_match %>%
  mutate(watershed_toolik_all = case_when(
    template %in% c("VSS", "TN", "DIN", "TP", "PO4", "TOC") ~ NA_character_,
    TRUE ~ watershed_toolik_all)))

lookup_table <- lookup_table %>%
  filter(!is.na(watershed_toolik_all))

correct_colnames <- lookup_table$template

```
New data table with only the columns that match the template

```{r}


new_datatable_toolik_all <- Toolik_watershed_with_duplicates %>% 
        select(all_of(c(correct_colnames)))

```

Loading the solute units template

```{r}


solute_units_Template <- read_excel(here("metajam_example", "Stream_Data_Template.xlsx"), sheet = "Solute Units" )

solute_units_Template <- solute_units_Template  %>%
  select(Measurement, Unit)


```
Making a dataframe from the attribute metadata that only inlcudes the columns I need to match the template (attributeName and units)


```{r}

attributes <- Toolik_watershed_data %>%
  select(Type, Units) %>%
  unique() %>%
  rename('Measurement' = 'Type')


#strip white space

attributes$Measurement <- trimws(attributes$Measurement, which = c("left"))

attributes$Measurement <- gsub("Calcium", "Ca", attributes$Measurement)
attributes$Measurement <- gsub('Silica', 'Si',attributes$Measurement)
attributes$Measurement <- gsub('Sodium', 'Na', attributes$Measurement)
attributes$Measurement <- gsub('Potassium', 'K', attributes$Measurement)
attributes$Measurement <- gsub('Magnesium', 'Mg', attributes$Measurement)
attributes$Measurement <- gsub('Carbon Dioxide', 'CO2', attributes$Measurement)
attributes$Measurement <- gsub('Total Dissolved Phosphorus', 'TDP', attributes$Measurement)
attributes$Measurement <- gsub('Dissolved Organic Carbon', 'DOC', attributes$Measurement)
attributes$Measurement <- gsub('Methane', 'CH4', attributes$Measurement)
attributes$Measurement <- gsub('Ammonium', 'NH4', attributes$Measurement)
attributes$Measurement <- gsub('Total Dissolved Nitrogen', 'TDN', attributes$Measurement)
attributes$Measurement <- gsub("Sestonic Chlorophyll a", 'Suspended Chl', attributes$Measurement)
attributes$Measurement <- gsub("Temp when sample collected", 'Temp', attributes$Measurement)
attributes$Measurement <- gsub("Specific Conductivity", 'Specific Conductance', attributes$Measurement)
attributes$Measurement <- gsub("Nickel", 'Ni', attributes$Measurement)
attributes$Measurement <- gsub("Chloride", 'Cl', attributes$Measurement)
attributes$Measurement <- gsub("Copper", 'Cu', attributes$Measurement)
attributes$Measurement <- gsub("Sulfate", 'SO4', attributes$Measurement)
attributes$Measurement <- gsub('Soluble Reactive Phosphorus', 'SRP', attributes$Measurement)
attributes$Measurement <- gsub('Total Suspended Sediment', 'TSS', attributes$Measurement)
attributes$Measurement <- gsub('Dissolved Inorganic Carbon', 'DIC', attributes$Measurement)




```

Fuzzy matching template solute units table to attribute table
```{r}

(fuzzy_match <- tibble(solute_units_Template$Measurement) %>%
   mutate(watershed_units = attributes$Measurement[amatch(tolower(solute_units_Template$Measurement), tolower(attributes$Measurement), maxDist = 1, weight = c(d=1,i=0.1,s=1,t=1))])
)


```


Fuzzy matching template solute units table to attribute table
```{r}

# Fill in the columns that didn't match, and correct the wrongly corrected matches
# continue in the same way until you've filled out everything you could.
  # Note: NA_character_ is just NA but of the character type.
(lookup_table_units <- fuzzy_match %>%
  mutate(attributes = case_when(
    solute_units_Template$Measurement %in% c("Q","DO", "DO%", "TKN", "TOC", "TN", "DON", "TP", "DOP", "PP", "PO4") ~ NA_character_, TRUE ~ watershed_units)))

#Make a string of the correct names
correct_names <- lookup_table_units$'solute_units_Template$Measurement'

```

```{r}


#Make a table that matches the template
solute_units_table_new <- attributes %>% 
        filter(Measurement %in% c(correct_names))

```

Export an excel workbook with two sheets

```{r}


## setup a workbook with 2 worksheets
wb <- createWorkbook()
addWorksheet(wb = wb, sheetName = "Raw Data (Sheet 1)", gridLines = FALSE)

writeDataTable(wb = wb, sheet = 1, x = new_datatable_toolik_all)

addWorksheet(wb = wb, sheetName = "Solute Units (Sheet 2)", gridLines = FALSE)

writeData(wb = wb, sheet = 2, x = solute_units_table_new)

saveWorkbook(wb, "ADC_Toolik_ALL_watershed.xlsx", overwrite = TRUE)

```