---
title: "ADC_toolik_dimple_inlet_watershed"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Step 1: Load packages

```{r}

library(metajam)  
library(udunits2)
# For wrangling the data
library(readr)
library(tidyr)
library(dplyr)
library(purrr)
library(stringr)
library(metajam)
library(tidyverse) # for convenience
library(here) # for file path management
library(stringdist) # for first pass of naming-matching
library(vctrs) # for joining tables
library(readxl) # for reading the template excel sheet
library(openxlsx) #for writing the excel file

```

####Step 2: Find the link to the dataset
Go to the web address for the dataset and find the download button for the data. 

In our case the link is: https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-arc.10303.6&entityid=bbc1cb59633df57380d997726916180a

#### Step 3: Choose where you want the files to be saved
In our case, we'll just put it into the metajam_example folder.

```{r}

#eg desired_path_to_data <- "~/Desktop"
desired_path_to_data <- "~/SI_river_data"

# create the folder if it does not exist yet
dir.create(desired_path_to_data, showWarnings = FALSE)


```

#### Step 4: Download the data by pasting the link you just copied
```{r}

my_data_url <- "https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-arc.10303.6&entityid=bbc1cb59633df57380d997726916180a"

# this will download the data into a folder and save the path to that folder
downloaded_data <- download_d1_data(data_url = my_data_url, path = desired_path_to_data)


```

#### Step 5: Now read in the data (with all the metadata)

```{r}


my_data <- read_d1_files(downloaded_data, na = c("-888.88", "-888.888", "-888", "-999", "-9999"))

Toolik_watershed_data <- my_data$data

#remove 2nd and 3rd rows which were empty
Toolik_watershed_data <-  Toolik_watershed_data[-c(1, 2, 3),]

```

#Data Cleanup


```{r}

Toolik_watershed_data$Type <- gsub("[^0-9A-Za-z///' ]","", Toolik_watershed_data$Type)

#removing cation preface
Toolik_watershed_data$Type <- gsub("Cations", "", Toolik_watershed_data$Type)

#strip white space

Toolik_watershed_data$Type  <- trimws(Toolik_watershed_data$Type, which = c("left"))


#Create a list of unique watershed names 
Toolik_stream_names <- unique(Toolik_watershed_data$River)

Toolik_stream_names 
#Adding a column to identify the LTER site - ARC

Toolik_watershed_data <- Toolik_watershed_data %>% 
  add_column(LTER = 'ARC', .before = "River")


Toolik_dimple_inlet_watershed <- Toolik_watershed_data %>% 
  filter(River == "Dimple Inlet")

```



```{r}


#in this data set there are duplicate measurements for the same attribute on the same day at the same time




#Changing from long format to wide format like template
Toolik_dimple_inlet_watershed  <- spread(Toolik_dimple_inlet_watershed, key = 'Type', value = 'Value')






```

